Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-12-13 latex/paper.tex
按照郭志新的意见修改

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-12-07 14:28:22

@@

\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2,1}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  The silicon materials present complex surface reconstructions, which are usually neglected for the thermal conductivity investigations due to their small specific surface area. However, the reconstruction effect can be significant when the material thickness becomes ultra thin, i. e., multilayer silicene. Here we systematically study the thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.  We find that the thermal conductivity of multilayer silicene present significant surface-structure dependence. The thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK depending on the specific surface structures. We also find that the surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  for the flour-layer  $2\times1$ silicene.  The anisotropy decreases with silicene thickness increasing, owing to the significant reduction of the thermal conductivity in the zigzag direction and its slight increment  in the armchair direction.
  Finally, we find that both the phonon-lifetime  anisotropy and the phonon-group-velocity  anisotropy contribute to the thermal conductivity anisotropy for the multilayer silicene.
  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials  with surface constructions in the future.

@@

Many theoretical and experimental results have shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them great potential in the applications of thermoelectrics. For example, the experiment of Boukai \emph{et al}.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values of approximately 100-fold improvement over bulk Si are achieved over a broad temperature range. Hochbaum \emph{et al}.\cite{Hochbaum2008} also proposed a way of increasing ZT by controling the roughness of silicene nanowires. At present, the thermal conductivity of the silicon nanostructures, i. e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a,Chen2016} had been well studied. However, the thermal conductivity of multilayer silicene is still mysterious.
The combined effects of quantum size and surface reconstruction in multilayer silicene is expected to induce exotic thermal transport properties different from both monolayer silicene and bulk Si,  which may make it suitable for the thermoelectric applications. Since the the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.

The existing research on thermal conductivity of  2D materials  mainly focus on the ones with weak Van der Waals(vdW) interlayer interaction where there is no surface reconstruction, such as multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015}.  Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation
\cite{Fu2014,Padova2016,Guo2015Structural}.
Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties\cite{Fu2014,Guo2015Structural}. Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity.
Especially, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  promotes the applications of covalently bonded 2D materials in the thermoelectrics.

In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various thickness  (2-10 atomic layers) and surface reconstructions in use of  the BTE method.  We find that the thermal conductivity of multilayer silicene is significantly affected by the surface reconstructions, which can induce  either ultralow thermal conductivity value ($3.3$ W/mK) or unusual high thermal conductivity anisotropy (70\%).  This feature shows that the  multilayer silicene is an ideal candidate in the thermoelectrics.

@@

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.95\linewidth]{structures.eps}
  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicene. Within which  are top view and side view of the studied structures. The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface. All the atoms on the bottom surface are labeled as blue. The greens represent those that are inside the structure. The orientation of top view of the cells is labeled as arrows.}
\end{figure}

Before thermal conductivity calculation, the  structures are fully optimized using the conjugate gradient (CG) method to make them stable.  Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thridorder respectively are applied to extract the second- and third-order force constants (FCs), in which hundreds of  slightly displaced supercells are generated. The obtained forces are calculated and used to calculate the FCs with numerical differential calculation. The chosen supercells are $3 \times 3 \times 1$ of premitive cells to make the in-plane dimension above 40 \angstrom, which ensures  the accuracy of calculated forces. Following to previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.

@@

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{tc_length_sheng.eps}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair. The dots of 2l2a and 2l2z are almost the same so red solid dots are covered. }
\end{figure}

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{chi.eps}{}
  \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{tc_freq.eps}
  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{tau.eps}
  \caption{\label{fig:tau} (color online) Lifetime of phonons considering three-phonon scattering for all the structures. }
\end{figure}

We then explore the contributions from the phonon lifetimes for the anisotropy.
We considered the three-phonon scattering process, where the phonon scattering rate could be obtained by the Fermi-golden rule\cite{Li2014} considering only the relaxation time approximation (RTA). The the iterative method was then used to include the cross influence of the phonon excitation, witch usually gives lager but more accurate lifetimes than the RTA. The frequency dependence of phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.  It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2l1, 2l3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity. Moreover, the lifetime in armchair direction is obviously larger than that in zigzag direction in the low-frequency region. This feature inidcates that the anisotropy in bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
On the other hand, the phonon lifetimes exhibit different frequency distributions in the thicker silicene, i. e.,  $2\times1$ structure with 3-6 Si layers, which cover both the low and high frequency regions with lifetimes  larger than 1 ps.  This is explains the high frequency phonons contribute significantly to the thermal conductivity in these structures (Fig. 4).  Except for the 4l1 structure, the lifetime distributions in zigzag and armchair directions are very similar for these  $2\times1$ structures, showing the tiny effect of phonon lifetimes on the anisotropy.

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{gv.eps}{}
  \caption{\label{fig:gv} (color online)Group Velocity versus phonon frequencies for both zigzag direction and armchair direction of the structures.The histogram bin width is chosen as 1.5THz.}
\end{figure}

To further explore the origin of thermal conductivity anisotropy in multilayer  silicene, we have calculated the frequency dependence of phonon group velocities. As shown in Fig. 6,  the group velocity  difference is very small in the low-frequency region for the bilayer silicene, confirming that the anisotropy mainly comes from the different phonon scattering effect in armchair and zigzag directions,  which induce different phonon lifetimes.
As for the $2\times 1$ silicene with thickness more than layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region. Combined with the fact that the lifetime difference contributes little to the anisotropy for 3l1, 5l1, and 6l1 structures, one can conclude that the group velocity difference is the main reason for the anisotropy of $2\times 1$ silicene structures. It should be noted that the anisotropy of 4l1 structure is from contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.

@@

\quad \\
\section{ACKNOWLEGEMENTS}
This paper was partially supported by the National Natural Science Foundation of China, the Special Funds for Major State Basic Research, the Foundation for the Author of National Excellent Doctoral Dissertation of China, the Program for Professor of Special Appointment at Shanghai Institutions of Higher Learning, and the Research Program of Shanghai Municipality and the Ministry of Education.

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-12-13 15:17:11

@@

\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Zhi-Xin Guo${}^{2,1}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  The silicon materials present complex surface reconstructions, which are usually neglected for the thermal conductivity investigations due to their small specific surface area. However, the reconstruction effect can be significant when the material thickness becomes ultra thin, i. e., multilayer silicene. Here we systematically study the thermal conductivity of multilayer silicene by means of Boltzmann Transportation Equation (BTE) method.  We find that the thermal conductivity of multilayer silicene present significant surface-structure dependence. The thermal conductivity of bilayer silicene varies from $3.31$ W/mK to $57.9$ W/mK depending on the specific surface structures. We also find that the surface reconstruction induces unusual large thermal conductivity anisotropy, which reaches 70\%  for the four-layer  $2\times1$ silicene.  The anisotropy decreases with silicene thickness increasing, owing to the significant reduction of the thermal conductivity in the zigzag direction and its slight increment  in the armchair direction.
  Finally, we find that both the phonon-lifetime  anisotropy and the phonon-group-velocity  anisotropy contribute to the thermal conductivity anisotropy for the multilayer silicene.
  This work could be helpful in the field of heat management, thermoelectric applications involving silicene and other multilayer nanomaterials  with surface constructions in the future.

@@

Many theoretical and experimental results have shown that quantum confinement and surface effects could reduce thermal conductivity remarkably while remain the electric conductivity remain at a relatively high level, which made them great potential in the applications of thermoelectrics. For example, the experiment of Boukai \emph{et al}.\cite{Boukai2008} shows that by varying the nanowire size and impurity doping levels, ZT values of approximately 100-fold improvement over bulk Si are achieved over a broad temperature range. Hochbaum \emph{et al}.\cite{Hochbaum2008} also proposed a way of increasing ZT by controling the roughness of silicene nanowires. At present, the thermal conductivity of the silicon nanostructures, i. e.,  silicene nanowires\cite{Hochbaum2008,Yang2010,Shi2009,Boukai2008} and monolayer silicene\cite{Pei2013,Ng2013,Xie2014,Zhang2014,Liu2014,Wang2015,Zhang2015a,Chen2016} had been well studied. However, the thermal conductivity of multilayer silicene is still mysterious.
The combined effects of quantum size and surface reconstruction in multilayer silicene is expected to induce exotic thermal transport properties different from both monolayer silicene and bulk Si,  which may make it suitable for the thermoelectric applications. Since the thermal conductivity of monolayer silicene and  bulk Si have been well explored, investigation on multilayer silicene is also helpful for understanding the thermal conductivity  evolution from two dimensional (2D) to three dimensional (3D) systems.

The existing research on thermal conductivity of  2D materials  mainly focus on the ones with weak Van der Waals(vdW) interlayer interaction where there is no surface reconstruction, such as multilayer graphene\cite{Lindsay2011,Ni2012,Wang2011}, $MoS_2$\cite{Liu2015}, and black phosphorus\cite{Zhang2015,Peng2015,Jain2015}.  Whereas, the thermal conductivity of 2D materials with strong interlayer interactions have been barely explored.
The multilayer silicene which has been both theoretically predicted and experimentally synthesized can be an ideal material for such an investigation \cite{Fu2014,Padova2016,Guo2015Structural}.
Previous studies  showed that the mutilayer silicene exhibit special surface reconstructions which induces the intriging electronic properties\cite{Fu2014,Guo2015Structural}. Naturally, one can expect that  the surface reconstruction is a significant factor for the thermal conductivity. Both experiments and theory suggests surface reconstruction in 2D materials may induce large anisotropy, for example, BP and phosphorene exhibit distinct orthogonal electrical and thermal transport anisotropies arising from their puckered structure \cite{Zhang2015,Peng2015}. While the anisotropic electrical properties influence the device performance, the anisotropic thermal transport properties are closely relevant to the thermomechanical reliability of functional devices fabricated from these materials. In particular, alternative flexible substrate and active layer materials with increased thermal conductivity are needed to prevent thermomechanical failures that have become an important challenge in flexible devices based on 2D materials\cite{Akinwande2014,Sadeghi2016}. Without doult, revealing the surface reconstruction effect on thermal conductivity anisotropy  in mutilayer silicene  could promote the applications of covalently bonded 2D materials in the thermoelectrics.

In this work, we systematically study the in-plane thermal conductivity of multilayer silicene with various thickness  (2-8 atomic layers) and surface reconstructions in use of  the BTE method.  We find that the thermal conductivity of multilayer silicene is significantly affected by the surface reconstructions, which can induce  either ultralow thermal conductivity value ($3.3$ W/mK) or unusual high thermal conductivity anisotropy (70\%).  This feature shows that the  multilayer silicene is an ideal candidate in the thermoelectrics.

@@

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.95\linewidth]{images/structures.eps}
  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicene. Within which  are top view and side view of the studied structures. The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface. All the atoms on the bottom surface are labeled as blue. The greens represent those that are inside the structure. The orientation of top view of the cells is armchair in the x direction and zigzag in the y direction in the figure.}
\end{figure}

Before thermal conductivity calculation, the  structures are fully optimized using the conjugate gradient (CG) method to make them stable.  Then finite displacement method (FDM) realized in Phonopy\cite{Togo2008} and Thirdorder respectively are applied to extract the second- and third-order force constants (FCs), in which hundreds of  slightly displaced supercells are generated. The obtained forces are calculated and used to calculate the FCs with numerical differential calculation. The chosen supercells are $3 \times 3 \times 1$ of premitive cells to make the in-plane dimension above 40 \angstrom, which ensures  the accuracy of calculated forces. Following to previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the interlayer thickness.

@@

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{images/tc_length_sheng.eps}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicene. b) The dependence on length of thermal conductivity for silicene with several layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.(\ref{eq:eq_nemd}). The letter z/a in the legend mean the transport direction is zigzag/armchair. The dots of 2l2a and 2l2z are almost the same so red solid dots are covered. }
\end{figure}

\begin{figure}[b]
  \includegraphics[angle= 0, width=0.9\linewidth]{images/chi.eps}{}
  \caption{\label{fig:chi} (color online) The anisotropy value dependence on length calculated with Eq.(\ref{eq:eq_chi})}
\end{figure}

@@

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{images/tc_freq.eps}
  \caption{\label{fig:tc_freq} (color online)  The converged thermal conductivity versus phonon frequency of the structures. }
\end{figure}

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{images/tau.eps}
  \caption{\label{fig:tau} (color online) Lifetime of phonons considering three-phonon scattering for all the structures. }
\end{figure}

We then explore the contributions from the phonon lifetimes for the anisotropy.
We considered the three-phonon scattering process, where the phonon scattering rate could be obtained by the Fermi-golden rule\cite{Li2014} considering only the relaxation time approximation (RTA). The the iterative method was then used to include the cross influence of the phonon excitation, witch usually gives lager but more accurate lifetimes than the RTA. The frequency dependence of phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}, where the values are averaged for frequency bins to reduce complexity.  It is shown that the lifetimes of larger than 1 ps for bilayer silicene structures (2l1, 2l3) distribute on the low-frequency region, indicating the dominating contributions of low-frequency phonons to the thermal conductivity. Moreover, the lifetime in armchair direction is obviously larger than that in zigzag direction in the low-frequency region. This feature inidcates that the anisotropy in bilayer silicene is attributed to the difference of phonon lifetimes in different directions.
On the other hand, the phonon lifetimes exhibit different frequency distributions in the thicker silicene, i. e.,  $2\times1$ structure with 3-6 Si layers, which cover both the low and high frequency regions with lifetimes  larger than 1 ps.  This is explains the high frequency phonons contribute significantly to the thermal conductivity in these structures (Fig. \ref{fig:tc_freq}).  Except for the 4l1 structure, the lifetime distributions in zigzag and armchair directions are very similar for these  $2\times1$ structures, showing the tiny effect of phonon lifetimes on the anisotropy.

\begin{figure}[b]
  \includegraphics[width=0.9\linewidth]{images/gv.eps}{}
  \caption{\label{fig:gv} (color online)Group Velocity versus phonon frequencies for both zigzag direction and armchair direction of the structures.The histogram bin width is chosen as 1.5THz.}
\end{figure}

To further explore the origin of thermal conductivity anisotropy in multilayer  silicene, we have calculated the frequency dependence of phonon group velocities. As shown in Fig. \ref{fig:gv},  the group velocity  difference is very small in the low-frequency region for the bilayer silicene, confirming that the anisotropy mainly comes from the different phonon scattering effect in armchair and zigzag directions,  which induce different phonon lifetimes.
As for the $2\times 1$ silicene with thickness more than layers,  the group velocity in zigzag direction is obviously larger than that in the armchair direction in most of the frequency region. Combined with the fact that the lifetime difference contributes little to the anisotropy for 3l1, 5l1, and 6l1 structures, one can conclude that the group velocity difference is the main reason for the anisotropy of $2\times 1$ silicene structures. It should be noted that the anisotropy of 4l1 structure is from contributions of both phonon lifetime and group velocity, which lead to its unusual large anisotropy up to 70\%.

@@

\section{ACKNOWLEDGEMENTS}
This paper was partially supported by the National Natural Science Foundation of China, the Special Funds for Major State Basic Research, the Foundation for the Author of National Excellent Doctoral Dissertation of China, the Program for Professor of Special Appointment at Shanghai Institutions of Higher Learning, and the Research Program of Shanghai Municipality and the Ministry of Education.
